Exploring the conformational dynamics of a large molecule in solution using an external electric field: A nonequilibrium molecular dynamics simulation

### 2013-11-09 writedown/npt-neq/alanine.tex
a lot of changes according to Giovanni.

In this perspective, molecular dynamics (MD) has been proven useful in
understanding the behavior of a protein 
in both static and oscillatory EF~\cite{budi2005electric, budi2007effect, budi2008comparative,
  toschi2008effects, astrakas2011electric, astrakas2012structural,
  damm2012can, starzyk2013proteins, english2009nonequilibrium,
  solomentsev2012effects}. In these studies, the initial
configurations are usually taken from the Protein Data Bank (PDB),
and then temperature controlled simulations are performed for a maximum
time range of the order of 10-60 nanoseconds.
During this simulation time 
relevant conformational changes characterizing the solvated molecule can be observed. 
Along the trajectories, various observable, such as the
secondary structure, root mean square displacement (RMSD), the dipole
moment, shape parameters are calculated as a function of time, or
in stationary condition, taking time averages.
This approach releases useful information on how the
secondary structure of the molecule is changed by external  EF.  However,
the behavior of observables in time is characterized by 
strong
fluctuations. The entity of the fluctuations is such that a quantitative 
analysis becomes difficult and does not allow for  a clear understanding of the rationale behind the conformational changes.
A time average can reduce the statistical uncertainty,
but in non-stationary conditions, it is a not-well-founded procedure.
In fact, we are studying non-stationary nonequilibrium process
(e.g. relaxing process to the new conformations under a static
EF, or the dynamics from one conformation to the other under an oscillatory EF).
In this perspective, if one wants to use MD, the proper way to do it would be that of treating a situation of nonequilibrium with algorithms that can explicitly describe it.
This is the approach that will be followed in this work, using
the dynamical nonequilibrium molecular dynamics simulation (D-NEMD).
The method, firstly developed by one of us and coworkers~\cite{ciccotti1975direct, ciccotti1979thought}, 
has been recently applied, to the study of
hydrodynamics~\cite{orlandini2011hydrodynamics,
  orlandini2011hydrodynamics-01}. The essential feature of D-NEMD is to
provide a way of evaluating time-dependent
nonequilibrium averages starting from a properly determined initial ensemble.
In this context, the method can be used to analyze the
conformational changes of a solvated molecule, subject to a time-dependent EF.
In the present paper, we study a small peptide, alanine dipeptide, as a model for showing how the method can be used. 
The choice of a small peptide, rather than a larger one, is done firstly because it
is easier to draw clear conclusions on the nonequilibrium properties
of a single peptide by excluding the slow-going interplay between
different peptide segments along a chain.
Secondly, the computational cost required is rather massive and thus  testing
the various methodology proposed here would be hampered for large molecules,
although they remain our goal.

The paper is organized as follows:
We firstly describe the idea of D-NEMD, then
introduce the physical
observables chosen to analyze the nonequilibrium responses.
The numerical results for the response of alanine
dipeptide under static and oscillatory EF are
finally presented. By calculating the nonequilibrium properties from D-NEMD
simulations, we are able to address
a few relavant questions: (i)~How the conformation of the peptide
changes in an EF (conformational space);
(ii)~When do these changes happen (time scale),
and how likely they are (probability). 
To our knowledge, this study is one of the few (if not the first)  where
time-dependent nonequilibrium w.r.t. conformation
is explicitly considered for a large molecule
in solution subject to time-dependent EF.

@@

\begin{figure}
  \centering
  \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
  \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
  \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
  \caption{The probability of the conformations of the alanine dipeptide plotted on the Ramachandran histogram.
    (a): the
    equilibrium state at $t=0$~\textsf{ps}. (b): The new equilibrium
    state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
    action of a constant EF of 1~V/nm.  Darker color
    indicates higher probability.}
  \label{fig:tmp4}
\end{figure}

For each branching trajectory,  the molecular configuration of alanine is projected on
the Ramachandran histogram, as
shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
conformations is given in plot (a), and the fully relaxed
conformation under the action of $E_{\infty} = 1$~V/nm is given in plot (b).  It is
evident from the plot that the conformations are grouped in several clusters, and the
position of the clusters does not change when the external electric
field is applied.
% {\bf LUIGI COMMENT: HAN below is really not clear}\\
% This means that only few of the total of conformations are likely to be visited,
% in the nonequilibrium process.
% These conformations are called ``metastable states''.
% The strict definition of the
% metastability is not exactly the same as those conformations that are likely to be observed.
% Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
% we do not distinguish the definations, and assume they have the same meaning.
% {\bf END COMMENT}\\
For the sake of clarity, we divide the
Ramachandran histogram into 5 subregions, see Fig.~\ref{fig:tmp4},
then the analysis of conformations on the Ramachandran histogram is reduced to the
analysis of the 5 ranges of conformations, i.e. $\{A_1, A_2, B_1, B_2, C\}$,
or in short we call them conformations (the precise meaning is clear
from the context).
In this paper we use:
$A_1 = \{(\phi, \psi) | -134 \leq \phi <  13, -125 \leq \psi < 74\}$,
$A_2 = \{(\phi, \psi) |  128 \leq \phi <-134, -125 \leq \psi < 74\}$,
$B_1 = \{(\phi, \psi) | -110 \leq \phi <  13,   74 \leq \psi <-125\}$,
$B_2 = \{(\phi, \psi) |  128 \leq \phi <-110,   74 \leq \psi <-125\}$,
$C   = \{(\phi, \psi) |   13 \leq \phi < 128, -180 \leq \psi < 180\}$.
Considering the periodic bondary condition, if we write, for example,
$128 \leq \phi <-134$, it means that $\phi$ is in either range
$128 \leq \phi < 180$ or in $-180 \leq \phi < -134$.
These conformations
correspond to different secondary structures of a peptide chain:
$A_1$ and $A_2$ are
corresponding to the alpha helix. $B_1$ and $B_2$ are
corresponding to the beta sheet. $C$ is corresponding to the
left-handed alpha helix.

From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
range of conformations changes when the external EF is applied.
For instance, the population of conformation $C$ vanishes in equilibrium,
but plays an important role when the EF is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast the change is, and the relations to the 
the EF. 
First, we calculate the probability of being in a certain conformation range,
defined as:
\begin{align}
  P_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
Notice that the probability is time dependent, being an observable in nonequilibrium situation.
% which is the time dependent probability of the alanine being in metastable
% state $I$.
% Secondly, we study the
% forward and backward transition probability of the metastable conformations, which is defined by
% \begin{align}
%   P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
%   P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
%   % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
% \end{align}
% where $\Delta t$ is the time-scale of the observation.
% For a revserible and homogeneous Markov process, it is easy to show
% that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
% process considered by the present work, this relation is genarlly not guarenteed.
Second,
we study the net probability flux from conformation $I$ to $J$, defined by:
\begin{align}\nonumber
  F_{J,I}(t) & = \frac1{\Delta t}\, [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
  & J,I \in \{A_1, A_2, B_1, B_2, C\}.
\end{align}
Here the time interval $\Delta t$ should be small enough comparing with the
time scale of conformational dynamics,
so that the changes in the conformation probabilities
can be linearly approximated.
In the meanwhile,  $\Delta t$ should also be  large enough comparing with
the timestep of MD integrator, 
so that the left hand of Eq.~\eqref{eqn:tmp7} is well-defined, and can be
estimated with good statistical accuracy.
See also the discussions in Ref.~\cite{schuette2011markov}.
$F_{J,I}(t)$ is essentially the rate of how much conformation $J$ changes
into $I$ at time $t$. A positive value indicates the
net flux from $J$ to $I$,
while a negative value indicates a net flux from $I$ to $J$.
Through $F_{J,I}(t)$, the original overall nonequilibrium process $\vect x_t$
is reduced to the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
% If the resulting reduced process 
% is time-reversible, then it is obvious that
% $ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
% the irreversibility of the reduced process on
% $\{A_1, A_2, B_1, B_2, C\}$.
% In practice, to measure $ F_{J,I}(t)$, one needs first to approximate the limit
% in Eq.~\eqref{eqn:tmp7} by the finite difference,
% then calculate the joint probabilities on
% the right-hand-side from the molecular trajectories.
% In this context, for a precise finite difference approximation a smaller $\Delta t$ is
% preferable although the statistical uncertainty of measuring the joint probabilities
% is higher. In practice,
% we use a $\Delta t$ that is small enough for a precise finite difference approximation,
% and not small enough so that the joint probabilities can be calculated with acceptable accuracy.
In the case of oscillatory EF, the net probability flux is also highly oscillatory,
thus it is convenient to study the integrated probability flux:
\begin{align}
  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
\end{align}
this expresses the average over time of the effects of the EF on the conformation of the molecule.

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-meta-npt.eps}
  \caption{The probability that the system is in the ranges of conformations when a constant EF is present.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $A_1$,
    green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
    to $C$.
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-5.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
  \caption{
    The net probability flux and its integral, for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The first row shows the probability flux $F_{J,I}(t)$ in units of $\textrm{ps}^{-1}$, while the second
    shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (decreasing)
    $Q_{J,I}$ indicates positive (negative) net flux.
    From left to right, the five
    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$. 
    }
  \label{fig:tmp6}
\end{figure}

@@

The time-dependent probability of the system in a certain range of conformations is given in
Fig.~\ref{fig:tmp5}. The beta sheet conformations $B_1$ and $B_2$,
which are present at the initial stage after EF is switched on,
fade away as the system relaxes to the new equilibrium. The
probability of alpha helix $A_1$ conformation grows from 0.45 to 0.69.
Alpha helix $A_2$  does not change significantly  under the action of EF.
The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.

We plot the net probability fluxes and their integration in Fig.~\ref{fig:tmp6}.
Results show that for short $t$, the net fluxes are generally non-zero, however, 
as $t$ goes to infinity,
all fluxes converge to zero. This indicates
that as the EF is switched on, the system first is driven away from the initial
equilibrium (at zero EF);  This is a nonequilibrium process.
After a long enough time, the system
is fully relaxed to the new equilibrium defined by the action of the constant EF,
and stays there as long as the EF is kept.
% \\
% it gradually relaxes to the new equilibrium,
% {\bf COMMENT LUIGI: Not clear, because some of the states may not be visited again. Anyway the choice of name and definition of ``metastable'' sound really not great}\\
% For this reason we do not see any change
% in the population density of the metastable states.\\
% {\bf END COMMENT}\\

@@

    $F(t)$ is the net probability flux from conformation $I$ to $J$.

@@

    purple for $J=B_2$ and light blue for $J=C$. In a certain time interval,
    if the integrated flux $Q_{J,I}$ increases, there exists a (time-averaged)
    non-zero net flux from conformation $I$ to $J$.

>>>>

In this perspective, molecular dynamics (MD) has been proven useful in
understanding the behavior of a protein 
in both static and oscillatory EF~\cite{budi2005electric, budi2007effect, budi2008comparative,
  toschi2008effects, astrakas2011electric, astrakas2012structural,
  damm2012can, starzyk2013proteins, english2009nonequilibrium,
  solomentsev2012effects}. In these studies, the initial
configurations are usually taken from the Protein Data Bank (PDB),
and then temperature controlled simulations are performed for a maximum
time range of the order of 10-60 nanoseconds.
During this simulation time 
relevant conformational changes characterizing the solvated molecule can be observed. 
Along the trajectories, various observable, such as the
secondary structure, root mean square displacement (RMSD), the dipole
moment, shape parameters are calculated as a function of time, or
in stationary condition, taking time averages.
This approach releases useful information on how the
secondary structure of the molecule is changed by external  EF.  However,
the behavior of observables in time is characterized by 
strong
fluctuations. The entity of the fluctuations is such that a quantitative 
analysis becomes difficult and does not allow for  a clear understanding of the rationale behind the conformational changes.
A time average can reduce the statistical uncertainty,
but in non-stationary conditions, it is a not-well-founded procedure.
In fact, we are studying non-stationary nonequilibrium process
(e.g. relaxing process to the new conformations under a static
EF, or the dynamics from one conformation to the other under an oscillatory EF).
In this perspective, if one wants to use MD, the proper way to do it would be that of treating a situation of nonequilibrium with algorithms that can explicitly describe it.
This is the approach that will be followed in this work, using
the dynamical nonequilibrium molecular dynamics simulation (D-NEMD).
The method, firstly developed by one of us and coworkers~\cite{ciccotti1975direct, ciccotti1979thought, ciccotti1993theoretical, palla2008bulk}, 
has been recently applied, to the study of
hydrodynamics~\cite{orlandini2011hydrodynamics,
  orlandini2011hydrodynamics-01}. The essential feature of D-NEMD is to
provide a way of evaluating time-dependent
nonequilibrium averages starting from a properly determined initial ensemble.
In this context, the method can be used to analyze the
conformational changes of a solvated molecule, subject to a time-dependent EF.
In the present paper, we study a small peptide, alanine dipeptide, as a model for showing how the method can be used. 
The choice of a small peptide, rather than a larger one, is done firstly because it
is easier to draw clear conclusions on the nonequilibrium properties
of a single peptide by excluding the slow-going interplay between
different peptide segments along a chain.
Secondly, the computational cost required is rather massive and thus  testing
the various methodology proposed here would be hampered for large molecules,
although they \bluec{remain (\textit{does Giovanni write ``remain''? I cannot read})} our goal.

The paper is organized as follows:
\recheck{
  We firstly describe the idea of D-NEMD, and a local thermostating method
for nonequilibrium temperature control.
% Then
% introduce the physical
% observables chosen to analyze the nonequilibrium responses.
Then
after introducing the physical
observables chosen to analyze the nonequilibrium response,
the numerical results for the response of alanine
dipeptide under static and oscillatory EF are
finally presented.} By calculating the nonequilibrium properties from D-NEMD
simulations, we are able to address
a few relavant questions: (i)~How the conformation of the peptide
changes in an EF (conformational space);
(ii)~When do these changes happen (time scale),
and how likely they are (probability). 
To our knowledge, this study is one of the few (if not the first)  where
time-dependent nonequilibrium w.r.t. conformation
is explicitly considered for a \bluec{large molecule \textit{what does Giovanni write here? For me, the alanine dipeptide molecule is NOT large at all!}}
in solution subject to time-dependent EF.

@@

\begin{figure}
  \centering
  \includegraphics[width=1.00\textwidth]{fig-all-1.eps}
  % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
  % \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
  % \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
  \caption{
    \recheck{
    The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
    (a): An alanine dipeptide molecule.  Two dihedral angles
    $\phi$ and $\psi$ that are used to define the Ramachandran plot
    are shown with the molecule.
    (b): The equilibrium probability density on Ramachandran plot
    at $t=0$~\textsf{ps}. (c): The probability density of the new equilibrium
    state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
    action of a constant EF of 1~V/nm.  Darker color
    indicates higher probability.
    The Ramachandran plots are divided into 5 subregions corresponding
    to 5 molecular conformations:
    $A_1 = \{(\phi, \psi) | -134 \leq \phi <  13, -125 \leq \psi < 74\}$,
    $A_2 = \{(\phi, \psi) |  128 \leq \phi <-134, -125 \leq \psi < 74\}$,
    $B_1 = \{(\phi, \psi) | -110 \leq \phi <  13,   74 \leq \psi <-125\}$,
    $B_2 = \{(\phi, \psi) |  128 \leq \phi <-110,   74 \leq \psi <-125\}$,
    $C   = \{(\phi, \psi) |   13 \leq \phi < 128, -180 \leq \psi < 180\}$.
    Considering the periodic bondary condition, if we write, for example,
    $128 \leq \phi <-134$, it means that $\phi$ is in either range
    $128 \leq \phi < 180$ or in $-180 \leq \phi < -134$.
    This division is the same for both plot (b) and (c).
    }
  }
  \label{fig:tmp4}
\end{figure}

\recheck{
The time-dependent molecular conformations of alanine dipeptide are
investigated by estimate the probability density $p(\phi,\psi,t)$ on
the Ramachandran plot at time $t$. The definition of dihedral
angles $\phi$ and $\psi$ are given in Fig.~\ref{fig:tmp4}~(a).
The equilibrium probability density of
the conformations on the Ramachandran plot
is given in Fig.~\ref{fig:tmp4}~(b), and the fully
relaxed probability of conformations under
the action of $E_{\infty} = 1$~V/nm is
given in Fig.~\ref{fig:tmp4}~(c).  It is evident from the plot that
the probability density of conformations are grouped in several clusters,
% {\bf LUIGI COMMENT: HAN below is really not clear}\\
% This means that only few of the total of conformations are likely to be visited,
% in the nonequilibrium process.
% These conformations are called ``metastable states''.
% The strict definition of the
% metastability is not exactly the same as those conformations that are likely to be observed.
% Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
% we do not distinguish the definations, and assume they have the same meaning.
% {\bf END COMMENT}\\
therefore, for the sake of clarity, we divide the
Ramachandran histogram into 5 subregions $\{A_1, A_2, B_1, B_2, C\}$
(see the caption of Fig.~\ref{fig:tmp4} for definition), and
call each subregion, in short, a conformation of the alanine dipeptide. 
These conformations
are found in different secondary structures of a peptide chain:
$A_1$ and $A_2$ are
corresponding to the $\alpha$-helix. $B_1$ and $B_2$ are
corresponding to the $\beta$-sheet. $C$ is corresponding to the
left-handed $\alpha$-helix.
}
% In the end,
% the analysis of conformations on the Ramachandran plot is
% reduced to the analysis of the 5 conformations.

From Fig.~\ref{fig:tmp4}, it is obvious that the probability of
conformations changes when the external EF is applied.
For instance, the probability of conformation $C$ vanishes in equilibrium,
but plays an important role when the EF is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast the change is, and the relations to the 
the EF. 
Firstly, we calculate the probability
of each conformation:
\begin{align}
  P_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
Notice that the probability is time dependent, being an observable in nonequilibrium situation.
% which is the time dependent probability of the alanine being in metastable
% state $I$.
% Secondly, we study the
% forward and backward transition probability of the metastable conformations, which is defined by
% \begin{align}
%   P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
%   P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
%   % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
% \end{align}
% where $\Delta t$ is the time-scale of the observation.
% For a revserible and homogeneous Markov process, it is easy to show
% that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
% process considered by the present work, this relation is genarlly not guarenteed.
Secondly,
we study the net probability flux from conformation $I$ to $J$, defined by:
\begin{align}\nonumber
  F_{J,I}(t) & = \frac1{\Delta t}\, [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
  & J,I \in \{A_1, A_2, B_1, B_2, C\}.
\end{align}
\recheck{Where $\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I)$
is joint probability of the alanine being of conformation $J$ at
time $(t-\Delta t)$ \emph{and} being of conformation $I$ at time $t$.
A similar definition applies to $\mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)$.}
Here the time interval $\Delta t$ should be small enough comparing with the
time scale of conformational dynamics,
so that the changes in the conformation probabilities
can be linearly approximated.
In the meanwhile,  $\Delta t$ should also be  large enough comparing with
the timestep of MD integrator, 
so that the left hand of Eq.~\eqref{eqn:tmp7} is well-defined, and can be
estimated with good statistical accuracy.
See also the discussions in Ref.~\cite{schuette2011markov}.
% \recheck{$F_{J,I}(t)$ is essentially the time-dependent rate of
%   conformation change from $J$ to $I$.}
A positive value \recheck{of $F_{J,I}(t)$} indicates the
net flux from $J$ to $I$,
while a negative value indicates a net flux from $I$ to $J$.
Through $F_{J,I}(t)$, the original overall nonequilibrium process $\vect x_t$
is reduced to the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
% If the resulting reduced process 
% is time-reversible, then it is obvious that
% $ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
% the irreversibility of the reduced process on
% $\{A_1, A_2, B_1, B_2, C\}$.
% In practice, to measure $ F_{J,I}(t)$, one needs first to approximate the limit
% in Eq.~\eqref{eqn:tmp7} by the finite difference,
% then calculate the joint probabilities on
% the right-hand-side from the molecular trajectories.
% In this context, for a precise finite difference approximation a smaller $\Delta t$ is
% preferable although the statistical uncertainty of measuring the joint probabilities
% is higher. In practice,
% we use a $\Delta t$ that is small enough for a precise finite difference approximation,
% and not small enough so that the joint probabilities can be calculated with acceptable accuracy.
In the case of oscillatory EF, the net probability flux is also highly oscillatory,
thus it is convenient to study the integrated net probability flux:
\begin{align}\label{eqn:tmp7a}
  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
\end{align}
\redc{this expresses the cumulative effects of the EF
on the conformations of the molecule.}

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-meta-npt.eps}
  \caption{\recheck{The time-dependent probability of conformations $P_I(t)$} 
    when a constant EF is present.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = A_1$,
    green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
    to $C$. \recheck{Please notice that the summation of all conformational
      probabilities
    is identity, i.e.~$\sum_I P_I(t) = 1$.}
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-5.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
  \caption{
    The net probability flux and its integral, for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The first row shows the probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) in units of $\textrm{ps}^{-1}$, while the second
    shows the integrated  probability flux denoted by $Q_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7a}).
    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (decreasing)
    $Q_{J,I}$ indicates positive (negative) net flux.
    From left to right, the five
    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$. 
    }
  \label{fig:tmp6}
\end{figure}

@@

The time-dependent probability density of \bluec{the system \textit{what does Giovanni add here?} in} a certain
conformation is given in
Fig.~\ref{fig:tmp5}. The $\beta$-sheet conformations $B_1$ and $B_2$,
which are present at the initial stage after EF is switched on,
fade away as the system relaxes to the new equilibrium. The
probability of the $\alpha$-helix conformation $A_1$, grows from 0.45 to 0.69.
The $\alpha$-helix $A_2$  does not change significantly  under the action of EF.
The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.
We plot the net probability fluxes and their integration in Fig.~\ref{fig:tmp6}.
Results show that for short $t$, the net fluxes are generally non-zero, however, 
as $t$ goes to infinity,
all fluxes converge to zero. This indicates
that as the EF is switched on, the system first is driven away from the initial
equilibrium (at zero EF);  This is a nonequilibrium process.
After a long enough time, the system
is fully relaxed to the new equilibrium defined by the action of the constant EF,
and stays there as long as the EF is kept.
% \\
% it gradually relaxes to the new equilibrium,
% {\bf COMMENT LUIGI: Not clear, because some of the states may not be visited again. Anyway the choice of name and definition of ``metastable'' sound really not great}\\
% For this reason we do not see any change
% in the population density of the metastable states.\\
% {\bf END COMMENT}\\
\recheck{
Even though the system is finally relaxed to the new equilibrium,
the timescale of relaxation of each conformation is different. 
From Fig.~\ref{fig:tmp5} and \ref{fig:tmp6}, we observe mainly
three different timescales 10~ps, 100~ps and 500~ps,
as summarized in Tab.~\ref{tab:tmp1}.
}

@@

    $F_{J,I}(t)$ is the net probability flux from conformation $J$ to $I$.
    See also Eqn.~\eqref{eqn:tmp7} and~\eqref{eqn:tmp7a} for definitions
    of $F_{J,I}(t)$ and $Q_{J,I}(t)$, respectively.

@@

    purple for $J=B_2$ and light blue for $J=C$.
    \recheck{An increaseing $Q_{J,I}$ indicates a net probability
      flux from conformation $J$ to $I$,
      while a decreaseing $Q_{J,I}$ indicates a net probability
      flux from $I$ to $J$.
    % In a certain time interval,
    % if the integrated flux $Q_{J,I}$ increases, there exists a (time-averaged)
    % non-zero net flux from conformation $I$ to $J$.
